% - - - - - - - - - - -
% License: MIT
% - - - - - - - - - - -

\documentclass[12pt]{article}

\title{Curriculum Vitae}
\author{Bogdan Despotov}

\usepackage[english]{babel}
\usepackage{verbatim}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{ifthen}
\usepackage{titlesec}
\usepackage{enumitem}

% Font & encoding
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\input{glyphtounicode}
\pdfgentounicode=1

% Set layout and margins (H, V)
\geometry{letterpaper, margin={0.5in, 0.5in}}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Clear headers
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Format overrides
\titleformat{\section}{\scshape \Large \vspace{-5pt}}{}{0em}{}[\titlerule]

% Commands

\newcommand*{\header}[4]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \hspace{-5pt}\textbf{\LARGE{#1}} & \href{mailto:#2}{#2}\\
        \href{#3}{#3} & \href{tel:#4}{#4}
    \end{tabular*}\vspace{-5pt}
}

\newcommand*{\workSectionStart}[1]{\section{#1}\begin{itemize}[label={}, leftmargin=*]}

    \newcommand*{\workItem}[4]{\item
        \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
            \textbf{\large{#1}} & {#2}\\
            \slshape{#3} & \slshape{#4}
        \end{tabular*}
    }

    \newcommand{\workDataStart}{\begin{itemize}[label=$\circ$]\vspace{-4pt}}
        \newcommand*{\workDataItem}[2][]{\item\ifthenelse{\equal{#1}{}}{}{\textbf{#1:}} #2}
    \newcommand{\workDataEnd}{\end{itemize}}

\newcommand*{\workSectionEnd}{\end{itemize}}


\begin{document}

\header
    {Bogdan Despotov}
    {despotov@gmail.com}
    {https://github.com/bogdan-ds}
    {+359 899106450}


\workSectionStart{Experience}
    \workItem{Cognyte}{Bulgaria (remote)}
        {Machine Learning Engineer}{Mar. 2022 - Apr. 2023}
        \workDataStart
            \workDataItem[Ownership]{Responsible for all ML components: bug fixing, performance improvement, troubleshooting.}
            \workDataItem[Productionize]{Put to production as microservices ML models developed internally. Stack: Kubernetes, Helm, Flask, BentoML, GCP.}
            \workDataItem[Research]{Create PoCs for prospect client by fine-tuning state of the art ML models: YOLO, Whisper, easyOCR.}
            \workDataItem[Design]{Create high level designs for components that interact with the ML microservices, present to development teams and
                support their implementation efforts.}
        \workDataEnd

    \workItem{CloudSigma}{Sofia, Bulgaria (hybrid)}
        {Software Engineer}{Mar. 2016 - Mar. 2022}
        \workDataStart
            \workDataItem[Develop]{Worked on a proprietary cloud stack leveraging KVM, QEMU for virtualization. Included a customer facing API serving hunderds of thousands of requests daily.
                Leveraging a Python tech stack including: Django, Celery, Tastypie, unittest, Flask and more.}
            \workDataItem[Implementations]{Successfully implemented a number of new features including support for Intel SGX, GPUs, VMWare virtualization, SAML authentication.
                Helped reduce technical debt by refactoring legacy code, improving test coverage and transitioning from Python 2 to Python 3.}
            \workDataItem[EC projects]{Lead the technical involvement of the company in several project within the Horizon2020 and RISE frameworks.
                Efforts include software development, documentation and project management.}
        \workDataEnd

    \workItem{Hostway Corporation}{Sofia, Bulgaria}
        {Server support and administration, NOC monitoring}{Nov. 2011 - Jan. 2013}
        \workDataStart
            \workDataItem[Administration]{Within the product line of fully managed Linux and Windows servers.}
            \workDataItem[NOC]{Monitoring the global company network and servers and fixing issues as they arise.}
        \workDataEnd

\workSectionEnd


\workSectionStart{Education}
    \workItem{Sofia University "Kliment Ohridski"}{Sofia, Bulgaria}
        {Philosophy; Did not graduate}{Sept. 2014 - Sept. 2018}
\workSectionEnd

\workSectionStart{Projects}
    \workItem{\href{https://www.ditas-project.eu/}{DITAS}}{}
        {Data-intensive applications Improvement by moving data and compute in cloud}{Work package leader}
    \workItem{\href{https://project-cola.eu/}{COLA}}{}
        {Cloud Orchestration at the Level of Application}{Work package leader}
    \workItem{\href{https://www.securecloudproject.eu/}{SecureCloud}}{}
        {Secure Big Data Processing in Untrusted Clouds}{Part of consortium}
        \workDataStart
            \workDataItem[Publication Co-Author]{\href{https://ieeexplore.ieee.org/document/8513718}{Secure and Scalable Key Value Storage for Managing Big Data in
                Smart Cities using Intel SGX. }}
        \workDataEnd
    \workItem{\href{https://www.secincore.eu/}{SecInCore}}{}
        {Secure Dynamic Cloud based on Pan-European Disaster Inventory}{Part of consortium}
        \workDataStart
            \workDataItem[Publication Co-Author]{\href{https://ieeexplore.ieee.org/document/7934747}{Cloud-based semantic services for pan-European emergency preparation and planning}}
        \workDataEnd
    \workItem{\href{https://www.seo-dwarf.eu/}{SEO-DWARF}}{}
        {Semantic EO Data Web Alert and Retrieval Framework}{Part of consortium}

\workSectionEnd

\workSectionStart{Hobby Projects}
    \workItem{Logtrucks}{\href{https://github.com/bogdan-ds/logging}{Code}}
        {Logging trucks and license plates detection in the wild.}{}
        \workDataStart
            \workDataItem[Dataset]{Dataset of logs on trucks and Bulgarian license plates.}
            \workDataItem[Purpose]{To detect logging trucks and their license plates in the wild.}
            \workDataItem[Method]{Fine-tuned YOLOv7 and easyOCR on the datasets.}
        \workDataEnd
    \workItem{Bulgarian news comments dataset.}{\href{https://github.com/bogdan-ds/dnesbg\_dataset}{Code}}
        {Application to extract comments from a news site and build them into a dataset. }{}
        \workDataStart
            \workDataItem[Dataset]{Dataset of 500k comments on a news site in Bulgarian. }
            \workDataItem[Purpose]{Fine-tune LLaMa on the dataset mostly for comic effect. }
        \workDataEnd
    \workItem{Fine-tuned Llama 2 model for Bulgarian.}{\href{https://huggingface.co/bogdan1/llama2-bg}{Code}}
        {Llama 2 Base 7B fine-tuned for better Bulgarian language generation.}{}
        \workDataStart
            \workDataItem[Dataset 1]{Above mentioned news comments dataset.}
            \workDataItem[Dataset 2]{Chitanka dataset preformatted using this script: https://github.com/bogdan-ds/chitanka-llm-dataset}
        \workDataEnd

\workSectionEnd


\center{\tiny{\href{https://github.com/bogdan-ds/CV}{This CV was generated on \today}}
\end{document}
